### 2017-10-13 Gruba/01-intro.tex

Social media is overwhelming nowadays, with massive users on Facebook, Twitter and Weibo while the number of users keeps increasing.
These users behave variously, knowledge of which is significant in recommendation system, activity prediction and Big Thing analysis.
Hence emerges the demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.

Central to user behavior modeling, is the need to choose the granularity of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating users. 
Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

The key driver of our work is the realization that in social media applications, users could fall into groups and each group shares representative behaviors.
%
As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.
Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well. 
In the realm of social network behavior modeling, few work has been done over grouping, which however has been proved to be effective in other fields such as economic research.
This motivates us to explore the incorporation of user grouping into the \retg{} behavior modeling, filling the gap of existed studies in literature.

\stitle{Contributions.}
This work contributes as follows:

@@

\stitle{Organization.} The rest of this paper is organized as follows.
Section \ref{sec:overv} first gives the problem formulation and subsequently overviews \sys{}'s components, principle of which are detailed in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.
Section \ref{sec:perf} provides the performance evaluation.
Related work is presented in Section \ref{sec:rela}.
Finally, Section \ref{sec:conclu} concludes the work.

>>>>

Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, has attracted  massive users.
These users behave variously, knowledge of which is significant for various applications such as recommendation system and activity analysis.
Hence there is an emergent demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.

Central to user behavior modeling, is the need to choose the right granularity of model (i.e., how many users share one model), as well as the variety of features to be utilized for differentiating users.
Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

The key driver of our work is the observation that in social media applications, users could fall into groups and each group shares representative behaviors.
%
As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.
Particularly, we study the \retg{} behavior of users and our work can be readily generalized to other behaviors of like and comment as well.
In the realm of social network behavior modeling, few work has been done over grouping, which however has been proved to be effective in other fields such as economic behavior analysis.
This motivates us to incorporate user grouping into the \retg{} behavior modeling, filling the gap of existed studies that build a single model for all users.

The contributions of our work are as follows:

@@

Our paper is organized as follows.
Section \ref{sec:overv} first gives the problem formulation and subsequently overviews \sys{}'s components, principle of which are detailed in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.
Section \ref{sec:perf} provides the performance evaluation.
Related work is presented in Section \ref{sec:rela}.
Finally, Section \ref{sec:conclu} concludes the work.
